FoRTE baseline

### 2019-10-25 analysis/paper/paper.Rmd
Remove note about parameter interactions
Add intro Pandit paper text as discussion comment

{TODO: Basic analysis of contributions from parameter interactions, a la Raczka et al. 2018? I expect these will be important.}

@@

>>>>

@@

<!-- From Introduction: -->
<!-- Another recent study assessed parameter uncertainty in ED2 as part of its overall goal of parameterizing the model for sagebrush [@pandit_2018_optimizing]. -->
<!-- They found that the most important parameters were specific leaf area, the maximum rate of carbon fixation (V~cmax~), slope of stomatal conductance, the fine-root to leaf carbon ratio, and the fine root turnover rate. -->
